%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \documentclass[]{deedy-resume-openfont}
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Profile
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Stephen}{Schroeder}{stephenschroeder2013@gmail.com | 403 690 4109 | linkedin.com/in/stephenschroeder7 github.com/StephenSchroeder}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Education
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\runsubsection{BSc Honours in Geology}
\descript{| University of Calgary }
\location{Graduated April 2019 | Calgary, AB}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\textbf{Thesis Title:} Carbon Storage Dynamics of Saline lakes in the Cariboo Plateau, British Columbia
%\vspace{\topsep}

\begin{tightemize}
\item Analysed aqueous and mineral data using Python, Excel, and Geochemists’ Workbench
\item Modelled lake geochemistry and potential to sequester atmospheric CO$_{2}$
\item Prepared rock and aqueous samples for Optical Emission Spectrometry, Ion Chromatography, and X-Ray Diffraction analysis
\end{tightemize}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Experience
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\runsubsection{Undergraduate Researcher}
\descript{| University of Calgary}
\location{January 2019 - Present | Calgary, AB}
\textbf{Thesis Title:} Laboratory Constraints on the Kinetics of Pyrite Oxidation in Alkaline Waters
\begin{tightemize}
\item Grant-funded position to perform undergraduate research 
\item Responsible for experimental design, literature review, and geochemical modelling of pyrite oxidation. 
\end{tightemize}


\sectionsep

\runsubsection{Podcast Host}
\descript{| Endeavour Podcast}
\location{July 2018-Present | Calgary, AB}
Hosted a weekly podcast, interviewed professionals of diverse backgrounds and communicated their stories and science to the general public. Developed and maintained podcast hosting and social media.
\sectionsep

\runsubsection{Research Assistant}
\descript{| Paleoenvironmental Dynamics Group}
\location{Summer 2017, Summer 2018 | Heidelberg, Germany}
Supported research on Oligocene palaeoceanography and cryosphere modelling. Prepared, weighted, and diluted samples for ICP-OES analysis. 
\begin{tightemize}
\item Interpreted data and its relevance to the paleoclimate model using Excel
\item Identification of foraminiferal morphospecies under a microscope \item Analysis of microscope and stable isotope data using Excel 
\end{tightemize}
\sectionsep

\runsubsection{Student Assistant}
\descript{| University of Calgary}
\location{September 2016 – May 2017 | Calgary, AB}
Volunteered in a lab setting, supporting research on Swift Current Creek vertebrate fossil material.
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Skills
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills} 

\subsection{Programming}

\textbf{Python:} NumPy and Pandas data processing. Contributed to open-source packages on GitHub: PyJanitor, Econ-ARK, and Trio \\
\textbf{Wolfram Language:} Created a script which accesses the RunKeeper database in order to visualise my running history \\
\textbf{Excel:} Projects involving INDEX, MATCH and IF functions 
\sectionsep


\subsection{Professional}
Science Communication \textbullet{} Resource Estimation \textbullet{} Geologic Mapping \textbullet{} Petrographic Microscopy  \textbullet{}  \LaTeX 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards \& Honors} 
\runsubsection{Undergraduate Student Research Award}
\descript{}
\location{January 2019 | Natural Sciences and Engineering Research Council of Canada}
Awarded one of 3 competitive research grants available to the Geoscience department at the University of Calgary. The grant supported my research on pyrite oxidation.
\sectionsep

\runsubsection{RISE-Globalink Research Internship}
\descript{}
\location{May 2018 - August 2018 | MITACS \& German Academic Exchange Service}
One of the 60 Canadian highest ranked candidates to receive the RISE-Globalink scholarship, which allowed me to participate in a research project supervised by a doctoral student at the Heidelberg University.
\sectionsep

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Presentations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Presentations} 
\runsubsection{RISE Germany Presenter}
\location{August 2018 | Heidelberg, Germany}
Presented climate research and findings to a group of multidisciplinary students.
\sectionsep

\runsubsection{Undergraduate Research Night Presenter \\}
\location{December 2018 | Calgary,AB}
Helped undergraduate students aspiring to get involved in academic research.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Languages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Languages} 
%\descript{Native}
%English \\
\descript{Intermediate}
German \textbullet{} French
\sectionsep
